---
title: "R Notebook"
output: html_notebook
---

# Introduction

In this project, we will try to see if there is a relation between the intensity of care of cardiologists and
their vertical integration status.

First, we will set our environment up. We used discovery cluster for this project.

```{r setup, include=F}

library(remoter)
library(tidyverse)
library(parallel)
library(data.table)
library(fst)
library(comorbidity)
library(zeallot)
library(reshape)
library(dtplyr)
library(haven)
```

## An interface to use the cluster

```{r remoter setup}
knitr::knit_engines$set(remoter = function(options,port=8888) {
  code <- paste(options$code, collapse = '\n')
  out  <- capture.output(remoter::batch(script=code,port = port,timer = options$timer))
  knitr::engine_output(options, code, out)
})
```

```{remoter test, timer=F}
print("test okay")
```

# Setting up remote environment

We'll load the needed libraries:

```{remoter load libraries, include=F, timer=F}

numcores=62

library(tidyverse)
library(parallel)
library(data.table)
library(fst)
library(comorbidity)
library(zeallot)
library(reshape)
library(dtplyr)
library(haven)

setDTthreads(numcores)

```

# Calculations

### Choose columns and combine years

A function to choose the needed columns from our raw Medicare files and also combining all years in one file.

``` {remoter read personal data (MBFS) , timer=F}

#mbsf_2013=read.csv("/work/postresearch/Shared/Data_raw/Medicare/Claims/MBSF/den_saf_lds_5_2013.csv")
#mbsf_2014=read.csv("/work/postresearch/Shared/Data_raw/Medicare/Claims/MBSF/den_saf_lds_5_2014.csv")
#mbsf_2015=read.csv("/work/postresearch/Shared/Data_raw/Medicare/Claims/MBSF/den_saf_lds_5_2015.csv")
#mbsf_2016=read.csv("/work/postresearch/Shared/Data_raw/Medicare/Claims/MBSF/mbsf_lds_5_2016.csv")
#mbsf_2017=read.csv("/work/postresearch/Shared/Data_raw/Medicare/Claims/MBSF/mbsf_lds_5_2017.csv")
#mbsf_2018=read.csv("/work/postresearch/Shared/Data_raw/Medicare/Claims/MBSF/mbsf_lds_5_2018.csv")
#mbsf_2019=read.csv("/work/postresearch/Shared/Data_raw/Medicare/Claims/MBSF/mbsf_lds_5_2019.csv")
#mbsf_2020=read.csv("/work/postresearch/Shared/Data_raw/Medicare/Claims/MBSF/mbsf_lds_5_2020.csv")

mbsf_2013[10:15,]
#mbsf_2014[1:10,]
#mbsf_2015[1:10,]
#mbsf_2016[1:10,]
#mbsf_2017[1:10,]
#mbsf_2018[1:10,]
#mbsf_2019[1:10,]
#mbsf_2020[1:10,]

```


```{remoter choose columns, timer=F}
choose_columns = function(data_list,
                          columns = c(
                            "DESY_SORT_KEY",
                            "CLAIM_NO",
                            "LINE_NUM",
                            "CLM_THRU_DT",
                            "LINE_PLACE_OF_SRVC_CD",
                            "HCPCS_CD",
                            "LINE_ICD_DGNS_VRSN_CD",
                            "LINE_ICD_DGNS_CD",
                            "LINE_ALOWD_CHRG_AMT",
                            "PRF_PHYSN_NPI",
                            "PRVDR_SPCLTY",
                            "PRVDR_STATE_CD"
                          )) {
  require(data.table)
  data_list = lapply(data_list, function (data)
    data [, ..columns])
  result = rbindlist(data_list)
  return(result)
}

carrier_data_all_years = choose_columns(
  list(
    carrier_data_2013,
    carrier_data_2014,
    carrier_data_2015,
    carrier_data_2016,
    carrier_data_2017,
    carrier_data_2018,
    carrier_data_2019,
    carrier_data_2020
  )
)

carrier_data_all_years[, date := as.IDate(as.character(CLM_THRU_DT), "%Y%m%d")][order(date)]
write_fst(carrier_data_all_years, "carrier_data_all_years.fst")

outpatient_data_all_years = choose_columns(
  data_list = list(
    outpatient_data_2013,
    outpatient_data_2014,
    outpatient_data_2015,
    outpatient_data_2016,
    outpatient_data_2017,
    outpatient_data_2018,
    outpatient_data_2019,
    outpatient_data_2020
  ),
  columns = c("DESY_SORT_KEY", "CLM_THRU_DT", "CLM_TOT_CHRG_AMT")
)
outpatient_data_all_years[, date := as.IDate(as.character(CLM_THRU_DT), "%Y%m%d")][order(date)]
write_fst(outpatient_data_all_years, "outpatient_data_all_years.fst")

inpatient_data_all_years = choose_columns(
  data_list = list(
    inpatient_data_2013,
    inpatient_data_2014,
    inpatient_data_2015,
    inpatient_data_2016,
    inpatient_data_2017,
    inpatient_data_2018,
    inpatient_data_2019,
    inpatient_data_2020
  ),
  columns = c(
    "DESY_SORT_KEY",
    "CLM_THRU_DT",
    "CLM_TOT_CHRG_AMT",
    "CLM_DRG_CD"
  )
)
inpatient_data_all_years[, date := as.IDate(as.character(CLM_THRU_DT), "%Y%m%d")][order(date)]
write_fst(inpatient_data_all_years, "inpatient_data_all_years.fst")


```


Read this function's results if already done

```{remoter read all years data, timer=T}
carrier_data_all_years=read_fst("carrier_data_all_years.fst", as.data.table = T)
outpatient_data_all_years=read_fst("outpatient_data_all_years.fst", as.data.table = T)
inpatient_data_all_years=read_fst("inpatient_data_all_years.fst", as.data.table = T)
```

I will copy some data to my local machine to check my functions before running them in the cluster and on the main data.

```{remoter copy sample data, timer=F}
carrier_sample=carrier_data_all_years[1:100000]
inpatient_sample=outpatient_data_all_years[1:100000]
outpatient_sample=inpatient_data_all_years[1:100000]
s2c(carrier_sample)
s2c(inpatient_sample)
s2c(outpatient_sample)
```

##Yearly Calculators

These are the main functions that calculate yearly expenditures for patients and their corresponding physicians.\

### Diagnosis codes

First, we will add diagnosis codes from ICD and Medicare:

``` {r codes, include=F, timer=F}
  #diagnosis codes
  #from https://www.cms.gov/medicare-coverage-database/view/article.aspx?articleId=52850&ver=26 and https://www.aapc.com/codes/cpt-codes-range/93451-93533/10
  angio_codes=c(93451,93452,93453,93454,93455,93456,93457,93458,93459,93460,93461,93462,93463,93464
                ,93503,93505,93530,93531,93532,93533)
  #from https://www.cms.gov/medicare-coverage-database/view/article.aspx?articleid=57326&ver=13&keyword=electrocardiogram&keywordType=starts&areaId=all&docType=NCA,CAL,NCD,MEDCAC,TA,MCD,6,3,5,1,F,P&contractOption=all&sortBy=relevance&bc=1
  ecg_codes=c(93000,93005,93010,93040,93041,93042)
  #from https://scct.org/page/CardiacCTCodes include CTangio
  cardiac_ct_codes=c(75571,75572,75573,75574)
  #from https://cardiacmri.com/tech-guide/cpt-codes-relevant-to-cardiac-mri/
  cardiac_mri_codes=c(75557,75559,75561,75563,75565)
  # from https://medicarepaymentandreimbursement.com/2011/07/cardiovascular-stress-testing-cpt-93015.html and https://www.aapc.com/codes/cpt-codes-range/93000-93050/
  stress_test_codes=c(93015,93016,93017,93018)
  #from https://www.aapc.com/codes/cpt-codes-range/93303-93356/20     includes stress echo
  echocardiography_codes=c(93303,93304,93306,93307,93308,93312,93313,93314,93315,93316,93317,93318
                           ,93320,93321,93325,93350,93351,93356,93352,93355,93356)
  #from https://www.aapc.com/codes/cpt-codes-range/92920-92979/ and https://www.cms.gov/medicare-coverage-database/view/article.aspx?articleId=57479#:~:text=CPT%20codes%2092928%2C%2092933%2C%2092929,are%20assigned%20to%20APC%200104.    includes balloon and stent
  angioplasty_codes=c(92920,92921,92924,92925,92928,92929,92933,92934,92937,92938,92941,92943,92944
                      ,92973,92974,92975,92978,92979,93571,93572,"C9600","C9601","C9602","C9603"
                      ,"C9604","C9605","C9606","C9607","C9608")
  #from https://www.medaxiom.com/clientuploads/webcast_handouts/Coding_for_CABG-Open_Heart_Procedures.pdf and https://www.aapc.com/codes/cpt-codes-range/33016-33999/10    did not include 33517-33530 since these are used in conjunction with 33533-33548 and not alone, did not include 33542,33545,33548 since these are also in conjunction )aneurismectomy and vsd resection
  CABG_codes=c(33510,33511,33512,33513,33514,33516,33533,33534,33535,33536)
  #from http://www.icd9data.com/2015/Volume1/390-459/430-438/default.htm and https://www.icd10data.com/ICD10CM/Codes/I00-I99/I60-I69/I63-
  stroke_icd_9_codes=c(43301,43311,43321,43331,43381,43391,43401,43411,43491)
  office_visit_codes=c("99201","99202","99203","99204","99205","99211","99212","99213","99214"
                       ,"99215")
  IHD_icd_9_codes=c(410, 411, 412,413,414)
  IHD_icd_10_codes=c("I20", "I21", "I22", "I23", "I24", "I25")
  
```
\

### Patient yearly expenditures and use of services

I will first create a function that adds conditions of interest to the data.
```{r add conditions , timer = F }

yearly_calculator_patient_conditions = function(data) {
  
  #requirements
  require(data.table)
  require(dtplyr)
  require(tidyverse)
  require(lubridate)
  
  data %>%
    mutate(
      is_catheterization = HCPCS_CD %in% angio_codes,
      is_ecg = HCPCS_CD %in% ecg_codes,
      is_cardiac_ct = HCPCS_CD %in% cardiac_ct_codes,
      is_cardiac_mri = HCPCS_CD %in% cardiac_mri_codes,
      is_stress_test = HCPCS_CD %in% stress_test_codes,
      is_echocardiography = HCPCS_CD %in% echocardiography_codes,
      is_angioplasty = HCPCS_CD %in% angioplasty_codes,
      is_CABG = HCPCS_CD %in% CABG_codes,
      is_stable_angina = ifelse(
        LINE_ICD_DGNS_VRSN_CD == 0,
        LINE_ICD_DGNS_CD %in% c ("I208", "I209"),
        ifelse(LINE_ICD_DGNS_VRSN_CD == 9, LINE_ICD_DGNS_CD == "4139", NA)
      ),
      is_unstable_angina = ifelse(
        LINE_ICD_DGNS_VRSN_CD == 0,
        LINE_ICD_DGNS_CD == "I200",
        ifelse(LINE_ICD_DGNS_VRSN_CD == 9, LINE_ICD_DGNS_CD == "4111", NA)
      ),
      is_MI = if_else(
        LINE_ICD_DGNS_VRSN_CD == 0,
        substr(LINE_ICD_DGNS_CD, 0, 3) == "I21",
        if_else(
          LINE_ICD_DGNS_VRSN_CD == 9,
          substr(LINE_ICD_DGNS_CD, 0, 3) == "410" ,
          NA
        )
      ),
      is_cardiac_arrest = if_else(
        LINE_ICD_DGNS_VRSN_CD == 0,
        substr(LINE_ICD_DGNS_CD, 0, 3) == "I46",
        if_else(LINE_ICD_DGNS_VRSN_CD == 9, LINE_ICD_DGNS_CD == "4275", NA)
      ),
      is_stroke = if_else(
        LINE_ICD_DGNS_VRSN_CD == 0,
        substr(LINE_ICD_DGNS_CD, 0, 3) == "I63",
        if_else(
          LINE_ICD_DGNS_VRSN_CD == 9,
          LINE_ICD_DGNS_CD %in% stroke_icd_9_codes,
          NA
        )
      ),
      is_office_visit = LINE_PLACE_OF_SRVC_CD %in% office_visit_codes,
      is_cardiology_office_vist =
        (LINE_PLACE_OF_SRVC_CD %in% office_visit_codes) &
        (PRF_PHYSN_NPI %in% c("06", "C3")),
      is_IHD = if_else(
        LINE_ICD_DGNS_VRSN_CD == 0,
        substr(LINE_ICD_DGNS_CD, 0, 3) %in% IHD_icd_10_codes,
        if_else(
          LINE_ICD_DGNS_VRSN_CD == 9,
          substr(LINE_ICD_DGNS_CD, 0, 3) %in% IHD_icd_9_codes,
          NA
        )
      )
    ) %>%
    as.data.table()
}

a=yearly_calculator_patient_conditions(carrier_sample)
a
```

I will now summarise the data for each patient.
```{r summarise expenditures and uses}

summarise_expenditures = function(data, time_frame = 365, diagnosis){
  
  data%>%
    group_by(DESY_SORT_KEY) %>%
    filter(sum(eval(parse(
      text = paste("is_", diagnosis, sep = "")
    )), na.rm = T) == T) %>%
    mutate(first_diagnosis = min(date[eval(parse(text = paste("is_", diagnosis, sep = ""))) ==
                                        T]), na.rm = T) %>%
    mutate( had_IHD = (
      date - first_diagnosis < 0 &
        first_diagnosis - date < time_frame &
        is_IHD
    ))%>%
    filter(date - first_diagnosis >= 0 &
             date - first_diagnosis < time_frame &
             had_IHD == F,
           .preserve = T) %>%
    summarise(
      first_diagnosis = unique(first_diagnosis),
      tot_allowed_carrier = sum(na.rm = T, LINE_ALOWD_CHRG_AMT),
      office_visit_count = sum(na.rm = T, is_office_visit),
      cardiology_visit_count = sum(na.rm = T, is_cardiology_office_vist),
      distinct_clinicians = length(unique(PRF_PHYSN_NPI)),
      catheterization_count = sum(na.rm = T, is_catheterization),
      catheterization_cost = sum(na.rm = T, LINE_ALOWD_CHRG_AMT * is_catheterization),
      ecg_count = sum(na.rm = T, is_ecg),
      ecg_cost = sum(na.rm = T, LINE_ALOWD_CHRG_AMT * is_ecg),
      cardiac_ct_count = sum(na.rm = T, is_cardiac_ct),
      cardiac_ct_cost = sum(na.rm = T, LINE_ALOWD_CHRG_AMT * is_cardiac_ct),
      cardiac_mri_count = sum(na.rm = T, is_cardiac_mri),
      cardiac_mri_cost = sum(na.rm = T, LINE_ALOWD_CHRG_AMT * is_cardiac_mri),
      stress_test_count = sum(na.rm = T, is_stress_test),
      stress_test_cost = sum(na.rm = T, LINE_ALOWD_CHRG_AMT * is_stress_test),
      echocardiography_count = sum(na.rm = T, is_echocardiography),
      echocardiography_cost = sum(na.rm = T, LINE_ALOWD_CHRG_AMT * is_echocardiography),
      angioplasty_count = sum(na.rm = T, is_angioplasty),
      angioplasty_cost = sum(na.rm = T, LINE_ALOWD_CHRG_AMT * is_angioplasty),
      CABG_count = sum(na.rm = T, is_CABG),
      CABG_cost = sum(na.rm = T, LINE_ALOWD_CHRG_AMT * is_CABG),
      stable_angina = sum(is_stable_angina, na.rm = T) > 0,
      unstable_angina = sum(is_unstable_angina, na.rm = T) > 0,
      MI = sum(is_MI, na.rm = T) > 0,
      cardiac_arrest = sum(is_cardiac_arrest, na.rm = T) > 0,
      stroke = sum(is_stroke, na.rm = T) > 0,
      icd_9_pure = ifelse(prod(LINE_ICD_DGNS_VRSN_CD, na.rm = T) == 0, F, T),
      icd_10_pure = ifelse(sum(LINE_ICD_DGNS_VRSN_CD, na.rm = T) == 0, T, F)
    ) %>%
    group_by(DESY_SORT_KEY) %>%
    mutate(
      tot_cheap_prcdr = sum(
        ecg_count,
        stress_test_count,
        echocardiography_count,
        cardiology_visit_count
        ,
        na.rm = T
      ),
      tot_expensive_prcdr = sum(
        catheterization_count,
        cardiac_ct_count,
        cardiac_mri_count,
        angioplasty_count,
        CABG_count,
        na.rm = T
      ),
    )%>%
    as.data.table()
}

summary = summarise_expenditures(a , diagnosis = "stable_angina")

```

### Adding comorbidities

Here, I will add patient comorbidity scores.
```{r comorbidities}

comorbidity_finder=function(data, summary_data, time_frame = 365){

  require(comorbidity)
  
  #adding comorbidities
  comorbidity_and_phys_data =
    inner_join(data, summary_data[, c("DESY_SORT_KEY",
                                "first_diagnosis",
                                "icd_9_pure",
                                "icd_10_pure")], by = "DESY_SORT_KEY") %>%
    filter(date - first_diagnosis >= 0 &
             date - first_diagnosis < time_frame) %>%
    as.data.table()
  
  
  comorbidity_icd_9 = comorbidity_and_phys_data %>%
    subset(icd_9_pure == T)
  
  if (nrow(comorbidity_icd_9) != 0) {
    comorbidity_icd_9 = comorbidity(
      as.data.table(comorbidity_icd_9),
      id = "DESY_SORT_KEY",
      code = "LINE_ICD_DGNS_CD",
      score = "charlson",
      icd = "icd9",
      assign0 = T
    )
  }
  else {
    comorbidity_icd_9 = data.table(
      DESY_SORT_KEY = NA,
      score = NA,
      index = NA,
      wscore = NA,
      windex = NA
    )
  }
  
  comorbidity_icd_10 = comorbidity_and_phys_data %>%
    subset(icd_10_pure == T)
  
  if (nrow(comorbidity_icd_10) != 0) {
    comorbidity_icd_10 = comorbidity(
      as.data.table(comorbidity_icd_10),
      id = "DESY_SORT_KEY",
      code = "LINE_ICD_DGNS_CD",
      score = "charlson",
      icd = "icd10",
      assign0 = T
    )
  }
  else {
    comorbidity_icd_10 = data.table(
      DESY_SORT_KEY = NA,
      score = NA,
      index = NA,
      wscore = NA,
      windex = NA
    )
  }
  
 rbind(comorbidity_icd_9[, c("DESY_SORT_KEY", "score", "index", "wscore", "windex")]
                          , comorbidity_icd_10[, c("DESY_SORT_KEY", "score", "index", "wscore", "windex")])
}

comorbidity=comorbidity_finder(data = carrier_sample, summary_data = summary)
comorbidity
```

### Most common physicians for each patient

Now, we will find most common physicians and cardiologists for each patient.
```{r most common NPI}

#adding most common physicians
add_patient_NPI=function(data, summary_data, time_frame = 365){
    
  comorbidity_and_phys_data =
    inner_join(data, summary_data[, c("DESY_SORT_KEY",
                                "first_diagnosis",
                                "icd_9_pure",
                                "icd_10_pure")], by = "DESY_SORT_KEY") %>%
    filter(date - first_diagnosis >= 0 &
             date - first_diagnosis < time_frame) %>%
    as.data.table()
  
  patient_NPI_count_finder = function(data) {
    result = data %>%
      group_by(DESY_SORT_KEY, PRF_PHYSN_NPI) %>%
      summarise(n = n()) %>%
      arrange(.by_group = T, desc(n))
  }
  
  patient_NPI_counts = patient_NPI_count_finder(comorbidity_and_phys_data)
  
  patient_NPI_counts = left_join(patient_NPI_counts, distinct(data[, .(PRF_PHYSN_NPI, PRVDR_SPCLTY)]), by =
                                   "PRF_PHYSN_NPI")
  
  find_most_common = function(data) {
    data %>%
      group_by(DESY_SORT_KEY) %>%
      arrange(.by_group = T, desc(n)) %>%
      slice(1) %>%
      as.data.table()
  }
  find_most_common_by_specialty = function(data, specialty_code) {
    data %>%
      filter(PRVDR_SPCLTY %in% specialty_code) %>%
      group_by(DESY_SORT_KEY) %>%
      arrange(.by_group = T, desc(n)) %>%
      slice(1) %>%
      as.data.table()
  }
  
  most_common_physician = find_most_common(patient_NPI_counts)
  #primary care = 01:general practice/ family practice:08/ internal medicine:11/ geriatrics:38
  most_common_primary_care_physician = find_most_common_by_specialty(patient_NPI_counts,
                                                                     specialty_code = c("01", "08", "11", "38"))
  most_common_cardiologists = find_most_common_by_specialty(patient_NPI_counts, specialty_code =
                                                              "06")
  most_common_interventional_cardiologists = find_most_common_by_specialty(patient_NPI_counts, specialty_code =
                                                                             "C3")
  
  most_common_physician = data.frame(most_common_physician) %>%
    rename_with( ~ paste0("most_common_physician_", .x))
  most_common_primary_care_physician = data.frame(most_common_primary_care_physician) %>%
    rename_with( ~ paste0("most_common_primary_care_physician_", .x))
  most_common_cardiologists = data.frame(most_common_cardiologists) %>%
    rename_with( ~ paste0("most_common_cardiologist_", .x))
  most_common_interventional_cardiologists = data.frame(most_common_interventional_cardiologists) %>%
    rename_with( ~ paste0("most_common_interventional_cardiologist_", .x))
  
  summary_data = left_join(
    summary_data,
    most_common_physician,
    by = c("DESY_SORT_KEY" = "most_common_physician_DESY_SORT_KEY")
  )
  summary_data = left_join(
    summary_data,
    most_common_primary_care_physician,
    by = c("DESY_SORT_KEY" = "most_common_primary_care_physician_DESY_SORT_KEY")
  )
  summary_data = left_join(
    summary_data,
    most_common_cardiologists,
    by = c("DESY_SORT_KEY" = "most_common_cardiologist_DESY_SORT_KEY")
  )
  summary_data = left_join(
    summary_data,
    most_common_interventional_cardiologists,
    by = c("DESY_SORT_KEY" = "most_common_interventional_cardiologist_DESY_SORT_KEY")
  )%>%
    as.data.table()

  summary_data[, year_first_diagnosis := lubridate::year(first_diagnosis)]%>%
    as.data.table()

}

summary_with_npi=add_patient_NPI(data = carrier_sample, summary_data = summary)
summary_with_npi
```

## Physician integration status

Here, I will find which physicians are integrated.

```{r}

#calculate and add physician integration data
#this only uses visits to see if a physician is integrated or not (codde list)

physician_integration_finder = function(data,
                                        integrated_place_of_service_codes = c("19", "22"),
                                        all_place_of_service_codes = c("11", "19", "22"),
                                        integration_threshold = 0.5,
                                        code_list = c(
                                          "99201",
                                          "99202",
                                          "99203",
                                          "99204",
                                          "99205",
                                          "99211",
                                          "99212",
                                          "99213",
                                          "99214",
                                          "99215"
                                        )) {
  data = subset(data, HCPCS_CD %in% code_list)
  result = data %>%
    mutate(
      is_facility = LINE_PLACE_OF_SRVC_CD %in% integrated_place_of_service_codes,
      is_all = LINE_PLACE_OF_SRVC_CD %in% all_place_of_service_codes,
    ) %>%
    group_by(PRF_PHYSN_NPI, year) %>%
    summarise(
      in_facility_count = sum(is_facility, na.rm = T),
      in_all_count = sum(is_all, na.rm = T),
      tot = n(),
    ) %>%
    mutate(
      in_facility_prp = in_facility_count / in_all_count,
      in_facility_prp_from_tot = in_facility_count / tot,
      is_integrated = in_facility_prp >= integration_threshold,
      is_integrated_from_tot = in_facility_prp_from_tot >= integration_threshold,
    ) %>%
    as.data.table()
}

physician_integration_stats = physician_integration_finder(carrier_sample, integration_threshold =
                                                             0.5)
physician_integration_stats
```

This function will add the integration status of most common physicians to each patient's summary data.

```{r add integration}

#rename columns
rename_last = function(data, how_many, new_names) {
  total_cols = ncol(data)
  setnames(data, (total_cols - how_many + 1):(total_cols), new_names)
}
add_integration_status=function(data, physician_integration_stats){
  
  data = left_join(
    data,
    physician_integration_stats,
    by = c(
      "most_common_physician_PRF_PHYSN_NPI" = "PRF_PHYSN_NPI",
      "year_first_diagnosis" = "year"
    )
  ) %>% as.data.table()
  
  rename_last(
    data,
    7,
    c(
      "most_common_physician_in_facility_count"
      ,
      "most_common_physician_in_all_count"
      ,
      "most_common_physician_tot"
      ,
      "most_common_physician_in_facility_prp"
      ,
      "most_common_physician_in_facility_prp_from_tot"
      ,
      "most_common_physician_is_integrated"
      ,
      "most_common_physician_is_integrated_from_tot"
    )
  )
  
  data = left_join(
    data,
    physician_integration_stats,
    by = c(
      "most_common_primary_care_physician_PRF_PHYSN_NPI" = "PRF_PHYSN_NPI",
      "year_first_diagnosis" = "year"
    )
  ) %>% as.data.table()
  
  rename_last(
    data,
    7,
    c(
      "most_common_primary_care_physician_in_facility_count"
      ,
      "most_common_primary_care_physician_in_all_count"
      ,
      "most_common_primary_care_physician_tot"
      ,
      "most_common_primary_care_physician_in_facility_prp"
      ,
      "most_common_primary_care_physician_in_facility_prp_from_tot"
      ,
      "most_common_primary_care_physician_is_integrated"
      ,
      "most_common_primary_care_physician_is_integrated_from_tot"
    )
  )
  
  data = left_join(
    data,
    physician_integration_stats,
    by = c(
      "most_common_cardiologist_PRF_PHYSN_NPI" = "PRF_PHYSN_NPI",
      "year_first_diagnosis" = "year"
    )
  ) %>% as.data.table()
  
  rename_last(
    data,
    7,
    c(
      "most_common_cardiologist_in_facility_count"
      ,
      "most_common_cardiologist_in_all_count"
      ,
      "most_common_cardiologist_tot"
      ,
      "most_common_cardiologist_in_facility_prp"
      ,
      "most_common_cardiologist_in_facility_prp_from_tot"
      ,
      "most_common_cardiologist_is_integrated"
      ,
      "most_common_cardiologist_is_integrated_from_tot"
    )
  )
  
  
  data = left_join(
    data,
    physician_integration_stats,
    by = c(
      "most_common_interventional_cardiologist_PRF_PHYSN_NPI" = "PRF_PHYSN_NPI",
      "year_first_diagnosis" = "year"
    )
  ) %>% as.data.table()
  
  rename_last(
    data,
    7,
    c(
      "most_common_interventional_cardiologist_in_facility_count"
      ,
      "most_common_interventional_cardiologist_in_all_count"
      ,
      "most_common_interventional_cardiologist_tot"
      ,
      "most_common_interventional_cardiologist_in_facility_prp"
      ,
      "most_common_interventional_cardiologist_in_facility_prp_from_tot"
      ,
      "most_common_interventional_cardiologist_is_integrated"
      ,
      "most_common_interventional_cardiologist_is_integrated_from_tot"
    )
  )
  
  return(as.data.table(data))
}

add_integration_status(data = summary_with_npi, physician_integration_stats = physician_integration_stats)
```

```





  result = left_join(result, comorbidity_all, by = "DESY_SORT_KEY",) %>% as.data.table()



yearly_calcualtions_carrier_stable_angina=yearly_calculator(carrier_data_all_years,diagnosis="stable_angina")

yearly_calcualtions_carrier_unstable_angina=yearly_calculator(carrier_data_all_years,diagnosis="unstable_angina")

write_fst(yearly_calcualtions_carrier_stable_angina,"yearly_calcualtions_carrier_stable_angina.fst") 
write_fst(yearly_calcualtions_carrier_unstable_angina,"yearly_calcualtions_carrier_unstable_angina.fst")
